Gravitational Lens Recovery with \Glass: How to measure the mass profile and shape of a lens

### 2013-06-25 limits/ms.tex
New versions of main results plots with full error bars and with pixel-wise chi.
More edits.

\begin{abstract}
{\bf JR. Does \Glass\ stand for something?}\\
We introduce a new non-parametric gravitational lens modelling tool: \Glass. \Glass\ uses an adaptive grid of mass pixels to model the lens, searching through hundreds of thousands of models to marginalise over model uncertainties. It is built on a fully modular framework that can support different basis functions, while non-lensing data constraints -- for example stellar mass estimates from stellar population synthesis modelling, or stellar kinematic data -- can also be applied. As a first application, we apply \Glass\ to a suite of dynamically realistic mock N-body data to determine what quality of data -- strong lensing, stellar kinematics, and/or stellar masses -- are required to measure the circularly averaged mass profile of a lens and its shape. Our key findings are as follows: (i) for pure lens data, multiple sources with wide redshift separation give the strongest constraints as this breaks the well-known mass-sheet or steepness degeneracy; (ii) a single quad with time delays also performs well, giving a good recovery of both the mass profile and its shape; (iii) stellar masses -- for lenses where the stars dominate the central potential -- can also break the steepness degeneracy, giving a recovery almost as good as having time delay data or multiple source redshifts; (iv) stellar kinematics are similarly powerful if the data extend beyond the half light radius of the stars $r \gg r_{1/2}$ (required to integrate out the effect of the unknown velocity anisotropy, $\beta(r)$); and (v) if the lensing data already probe the mass profile over the region $r \sim r_{1/2}$, then stellar kinematic data can be used to probe $\beta(r)$ -- an interesting dynamic quantity in its own right. Where information on the mass distribution from lensing and other probes becomes redundant, this opens up the possibility of using strong lensing to constrain cosmological models. We will study this, and present the first results from \Glass\ applied to real data, in forthcoming papers.
\end{abstract}

@@

\section{Introduction}\label{sec:intro} %-----------------------------------------------------

{\bf JR. Lots of references missing here. Need to be added. But this should get us started.}\\

Since the discovery of the first gravitational lens
\citep{1979Natur.279..381W}, lensing has become an increasingly important probe
of the distribution of mass in the Universe
\citep{1937ApJ....86..217Z,2012arXiv1206.1225A}. Strong lensing in particular
provides a powerful probe of the mass distribution at the heart of galaxies and
galaxy clusters given good enough data
\citep{2010CQGra..27w3001B,2007ApJ...667..645R,2006ApJ...652L...5S,2009ApJ...690..154S}.
This in turn provides valuable constraints on the nature of dark matter
\citep{2006ApJ...652L...5S,2013ApJ...765...25N}, on cosmological models
\citep{2010Sci...329..924J, 2008ApJ...679...17C}, and on galaxy formation
models \citep{2012MNRAS.424..104L}. To date, some $\sim$400 strong lenses are
known\footnote{{\tt http://admin.masterlens.org/}.}, but with the advent of
large ground and space based surveys, many thousands of lenses are expected to
be discovered over the next ten years \citep{2012arXiv1206.1225A,
2010AAS...21540115M, 2004NewAR..48.1085K}.

The majority of lens modelling efforts to date have focussed on `parametric'
modelling, where simple theoretically motived models are fit using maximum
likelihood methods to the data \citep{2011A&ARv..19...47K, 1993A&A...273..367K,
2010GReGr..42.2151K}. This is useful in that a simple model provides valuable
physical insight. However, as data quality improves and the questions we ask of
these data become more refined, it is important to re-asses the impact of our
model assumptions. `Non-parameteric' methods -- that assume many more
parameters than the available data constraints -- are invaluable in this
respect. In non-parametric mass modelling, the lens inversion problem is
deliberately chosen to be under-constrained
\citep{1997MNRAS.292..148S,2005MNRAS.360..477D,2010ApJ...723.1678C,2006MNRAS.367.1209L,2013arXiv1304.2393S}.
Instead of finding one `best-fit' model, we must then search for many models
consistent with the data, exploring degeneracies between different but
plausible\footnotemark\ mass models
\citep{2000AJ....120.1654S,2006ApJ...653..936S,2008MNRAS.386..307L}. The key
advantages of non-parametric modelling are that we can: (i) explore model
degeneracies and marginalise over them; and (ii) we can determine what type and
quality of data (including data from stellar population synthesis modelling,
stellar kinematics, or other independent probes of the mass) are required to
measure parameters of interest.

\footnotetext{The word {\it plausible} encodes the key hidden gremlin in
non-parametric methods: constraints extra to the available data (priors) are
typically required on the solution space in order to make it finite. However,
even rather restrictive priors are far less restrictive than the implicit
constraints inherent in parametric mass modelling.}

In this paper, we use a new non-parametric strong lens modelling framework
\Glass\ to determine what quality and combination of lensing, stellar mass, and
stellar kinematic constraints best constrain the projected mass profile and
shape of a gravitational lens. This is particularly timely given the coming
explosion in strong lensing and complimentary data. Some significant work has
already proceeded in this direction in the literature.
\citet{2007ApJ...667..645R} were the first to test the recovery of strong
lensing surface density profiles using mock data generated from N-body models
{\bf JR. Is this true?}. They found that when including time delays, circularly
averaged surface density distributions can sufficiently well-recovered to make
interesting comparisons with theoretical models\footnote{Cosmological
parameters, however, are more sensitive. \citet{2007ApJ...667..645R} found that
over-restrictive model assumptions can lead to significant bias on the Hubble
parameter, $H_0$, for example, explaining earlier tensions reported in the
literature \citep[e.g.][]{2002astro.ph..4043K}.}. Since then, several groups
have used N-body mock data to explore the fidelity of strong lensing
reconstruction. \citet{2007MNRAS.380.1729L} explore the recovery of N-body
models using a new non-parametric genetic algorithm. Such comparisons were key
in the development of their novel `null-space' constraint that includes
information about where there a no images in addition to where there are
observed ones. XXX did YYY, finding ZZZ {\bf JR. I am sure there are many more
references that ought to be added here.}. Here, we expand on these earlier
works by considering not only the circularly averaged surface density profile
of a lens, but also its shape, higher order measures of the mass recovery (a
pixel-by-pixel comparison), and by considering the utility of wrapping in
constraints from stellar mass estimates, or stellar kinematics.

We use a new lensing tool, \Glass\, that uses an adaptive grid of mass pixels
to model the lens, generating thousands of models to marginalise over
uncertainties. \Glass\ shares some heritage with an earlier code, \PixeLens\
\citep{1997MNRAS.292..148S,2008ApJ...679...17C}, but differs in several
important respects:

This new functionality allows us to use model strong lens systems while
wrapping in additional data constraints. Linear constraints -- like the stellar
mass -- are applied simultaneously with the strong lensing constraints;
non-linear constraints are applied in a post-processing step, where models are
rejected using a likelihood analysis. This latter was prohibitively expensive
with \PixeLens\ as only up to $\sim$1000 models could be generated in a
reasonable time. With \Glass, we can routinely generate hundreds of thousands
of models such that we can afford to discard some if they are inconsistent with
independent data. In this first application of \Glass, we apply it to a suite
of dynamically realistic mock N-body data to test the recovery of the
circularly averaged mass profile of a lens and its shape. We will consider
using strong lensing as a cosmological probe, and present the first results
from \Glass\ applied to real data, in forthcoming papers.

@@

The lens equation:
%
\begin{equation}
\vec\beta = \vec\theta - \frac{D_{LS}}{D_S}\vec\alpha(\vec\theta)
\label{eqn:lens_equation}
\end{equation}
%
maps an observed image position $\vec\theta$ to a source position $\vec\beta$
via the correction factor \citep[e.g.][]{1992grle.book.....S}:
%
\begin{equation}
\vec\alpha(\vec\theta) = \frac{4GD_L}{c^2} \int \Sigma(\vec\theta')\frac{(\vec\theta - \vec\theta')}{\ |\vec\theta - \vec\theta'|^2}d^2\vec\theta'
\end{equation}
%
which accounts for the gravitational lensing effect of an intervening mass
(where $G$ is Newton's gravitational constant, and $c$ is the speed of light).
For our purposes we make use of the thin mass sheet approximation and assume
that the lensing mass is infinitely thin compared with the distance between the
source and the lens $D_{LS}$ and the lens and the observer $D_{L}$. These are
angular diameter distances where $D_* = (c/H_0)d_*$ and $d_*$ is a
dimensionless number that depends on cosmology.  The lens can then be thought
of as a projected surface density $\Sigma$ which diverts the path of a photon
instantaneously through the bending angle $\vec\alpha$.

@@

One way to understand the lens equation is via Fermat's principle. We can think of light as travelling only 
along extremum paths; lensed images only occur at the extrema of a virtual photon {\it arrival time surface} 
\citep{1986ApJ...310..568B}. The arrival (or travel) time $t$ of a virtual photon depends not only on the geometric
path it takes, but also on the general relativistic gravitational time dilation
due to the lens at a redshift of $z_L$.  In its complete form, with all units
and cosmology included we can write the arrival time as \citep{1986ApJ...310..568B}:
%
\begin{eqnarray}
N^2ct(\vec\theta) & = & (1+z_L)\frac{D_{L}D_{S}}{D_{LS}}\frac12 |\vec\theta - \vec\beta|^2 \nonumber \\
& & - (1+z_L)\frac{4GD_{L}^2}{c^2}\int \Sigma(\vec\theta') \ln |\vec\theta-\vec\theta'| d^2\vec\theta'
\label{eqn:full_arrival_time}
\end{eqnarray}
%
where the factor of $D_L^2$ in the second term comes from the fact that $\Sigma$
has units of \Msun/lyr$^2$. We can clean this up by writing down a dimensionless time
delay:
%
\begin{eqnarray}
\tau & = & \left[(1+z_L)D_{L}\right]^{-1}ctN^2 \nonumber \\
& = & \left[ (1+z_L) \frac{c}{H_0}d_L\right]^{-1}ctN^2 \nonumber \\
& = & \left[ (1+z_L) d_L\right]^{-1}\nu t
\label{tau}
\end{eqnarray}
%
in terms of our previous definitions. If we
further define a dimensionless density:
%
\begin{equation}
\kappa_\infty = \frac{4\pi G}{c^2}\frac{c}{H_0}d_L\Sigma
              = \frac{d_L}{\nu}\Sigma
\end{equation}
%
and a lensing potential:
%
\begin{equation}
\psi(\vec\theta) = \frac1\pi \int \kappa_\infty(\vec\theta') \ln|\vec\theta - \vec\theta'| d^2\vec\theta'\
\label{lensing potential}
\end{equation}
%
we can express \eqnref{eqn:full_arrival_time} very compactly as:
%
\begin{equation}
\tau(\vec\theta) = \frac12 \xi |\vec\theta-\vec\beta|^2 - \psi(\vec\theta)
\label{arrival time}
\end{equation}
%
where $\xi \equiv D_{S}/D_{LS}$. We explicitly write $\kappa_\infty$ to remind ourselves
that there is no source distance factor involved. This will be useful later when we consider
multiple sources.

If we think of $\tau$ as a surface then images will be observed wherever
$\nabla \tau = 0$. In other words, images obey Fermat's principle and appear at
extremums of the surface. Note that $\nabla \tau$ is just \eqnref{eqn:lens_equation} or:
\begin{equation}
  \xi \vec\beta = \xi \vec\theta - \frac 1\pi\int \kappa_\infty\frac{(\vec\theta - \vec\theta')}{\ |\vec\theta - \vec\theta'|^2}d^2\vec\theta'
\end{equation}

The only observables from \eqnref{arrival time} are the image positions, and
perhaps the stellar contribution to $\kappa_\infty$.  If the source object is
variable, however, then the observed light curves of each image will be
identical, but possibly shifted in time due to the different arrival times.
The time difference between identical portions of the light curves is called
the time delay $\Delta t$ between images.  Using \eqnref{tau} the time delay
$\Delta t_{21}$ between two images $\vec\theta_1$ and $\vec\theta_2$, where $\vec\theta_2$
arrives after $\vec\theta_1$, is $\Delta t_{21} = \Delta \tau_{21}(1+z_L)d_L /
\nu$. If $\beta$ and $\kappa_\infty$ were known exactly this would allow one
to precisely infer the Hubble constant. However, the source position is not
observable and the density distribution is highly degenerate.

@@

The trouble with solving the lens equation for the mass distribution is that the solutions are non-unique and degenerate -- many different solutions can give a statistically good reproduction of the data. To see why this is, it is instructive to simplify \eqnref{eqn:lens_equation} for a circularly symmetric lens: 
%
\begin{equation}
\vec\beta = \vec\theta - \frac{\theta_E^2}{\theta^2}\vec\theta
\label{eqn:lens_equation_circ}
\end{equation}
%
where $\theta = |\vec\theta|$, $\theta_E^2 = \frac{D_{LS}}{D_S D_L} \frac{4 GM(<\theta)}{c^2}$ is the Einstein radius, and $M(<\theta)$ is the mass enclosed within the images.

For sources on-axis (\vec\beta\ = \vec0), the images split into a degenerate Einstein ring with $\theta = \theta_E$. Even in this situation of maximal information (since the source position $\vec\beta$ cannot typically be known), there is a trivial degeneracy between $M(<\theta_E)$ and the angular diameter distances that depend on cosmological parameters (most strongly on the Hubble constant, $D_{L,S} \propto 1/H_0$). For fixed cosmology, a single source splitting into images in the most ideal situation gives us only an enclosed mass. This `steepness' degeneracy (also known as the mass-sheet degeneracy) generalises to the non-circularly symmetric case (CITES). Thus, to measure the mass profile of a lens, we require more information. This can come in the form of another source at different redshift that has its own Einstein radius, giving $M(<\theta_E')$. Or it can come in the form of additional constraints like time delay data between the images, stellar mass estimates from stellar populations synthesis modelling (CITE), stellar kinematics (CITE), or similar. However, even with further information, higher order degeneracies remain. XXX showed that there is a monopole degeneracy that allows additional mass to be deposited in-between images without any optical effect, while YYY find twisting degeneracies exist if ZZZ. These higher order degeneracies have a larger effect on shape measurement than the mass profile but remain largely uncharacterised in the literature. Further degeneracies enter also if there is a strong {\it external} field acting on the lens -- for example from a larger group or cluster environment within which the lens sits (CITES); this {\it shear term} can, in principle, however, be constrained by data (CITES). In \secref{sec:results}, we will use \Glass\ to determine how well such degeneracies can be broken by data of ever-increasing quality to measure the mass profile and shape of a lens. We assume throughout that the shear is negligible.

@@

@@

@@

\plottwo{ACchi2_profile.pdf}{BCchi2_profile.pdf}
\caption{The main results showing the quality of model recovery. Each panel corresponds to 
the named mock galaxy, whose parameters are listed in \tabref{mock galaxy params}. Within
each panel are six groups of results for each of six lens morphologies. Each morphology
considered the presence of time delays and a central image. The black markers are for tests
that did not include the stellar mass as a lower bound constraint, while the red markers
indicate where the stellar mass has been given.}
\label{main results}
\end{figure}

>>>>

\begin{abstract}
We use a new non-parametric gravitational -- \Glass -- to determine what quality of data (strong lensing, stellar kinematics, and/or stellar masses) are required to measure the circularly averaged mass profile of a lens and its shape. \Glass\ uses an under-constrained adaptive grid of mass pixels to model the lens, searching through thousands of models to marginalise over model uncertainties. Our key findings are as follows: (i) for pure lens data, multiple sources with wide redshift separation give the strongest constraints as this breaks the well-known mass-sheet or steepness degeneracy; (ii) a single quad with time delays also performs well, giving a good recovery of both the mass profile and its shape; (iii) stellar masses -- for lenses where the stars dominate the central potential -- can also break the steepness degeneracy, giving a recovery almost as good as having time delay data or multiple source redshifts; (iv) stellar kinematics are similarly powerful if the data extend beyond the half light radius of the stars $r \gg r_{1/2}$ (required to integrate out the effect of the unknown velocity anisotropy, $\beta(r)$); and (v) if the lensing data already probe the mass profile over the region $r \sim r_{1/2}$, then stellar kinematic data can be used to probe $\beta(r)$ -- an interesting dynamic quantity in its own right. Where information on the mass distribution from lensing and other probes becomes redundant, this opens up the possibility of using strong lensing to constrain cosmological models. We will study this, and present the first results from \Glass\ applied to real data, in forthcoming papers.
{\bf JR. Need to highlight also the shape recovery results here.} 
\end{abstract}

@@

\section{Introduction}\label{sec:intro} %-----------------------------------------------------
Since the discovery of the first gravitational lens
\citep{1979Natur.279..381W}, lensing has become an increasingly important probe
of the distribution of mass in the Universe
\citep{1937ApJ....86..217Z,2012arXiv1206.1225A}. Strong lensing in particular 
provides a powerful probe of the mass distribution at the heart of galaxies and
galaxy clusters \citep{2010CQGra..27w3001B,2007ApJ...667..645R,2006ApJ...652L...5S,2009ApJ...690..154S}, giving valuable constraints on the nature of dark matter \citep{2006ApJ...652L...5S,2013ApJ...765...25N}, cosmology 
\citep{2010Sci...329..924J, 2008ApJ...679...17C}, and galaxy formation \citep{2012MNRAS.424..104L}. To date, some $\sim$400 strong lenses are
known\footnote{{\tt http://admin.masterlens.org/}.}, but with the advent of
large ground and space based surveys, many thousands of lenses are expected to
be discovered over the next ten years \citep{2012arXiv1206.1225A,
2010AAS...21540115M, 2004NewAR..48.1085K}.

The majority of lens modelling efforts to date have focussed on `parametric'
modelling, where simple theoretically motived models are fit using maximum
likelihood methods to the data \citep{2011A&ARv..19...47K, 1993A&A...273..367K,
2010GReGr..42.2151K}. This is useful in that a simple model provides valuable
physical insight. However, as data quality improves and the questions we ask of
these data become more refined, it is important to re-asses the impact of our
model assumptions. `Non-parameteric' methods -- that assume many more
parameters than the available data constraints -- are invaluable in this
respect \citep{1997MNRAS.292..148S,2005MNRAS.360..477D,2010ApJ...723.1678C,2006MNRAS.367.1209L,2013arXiv1304.2393S}. Here, the lens inversion problem is
deliberately chosen to be under-constrained.
Instead of finding one `best-fit' model, we must search for many models
consistent with the data, exploring degeneracies between different but
plausible\footnotemark\ mass models
\citep{2000AJ....120.1654S,2006ApJ...653..936S,2008MNRAS.386..307L}. The key
advantages of non-parametric modelling are that we can: (i) explore model
degeneracies and marginalise over them; and (ii) we can determine what type and
quality of data are required to measure parameters of interest.

\footnotetext{Constraints extra to the available data are typically required on the solution space in order to make it finite. Such constraints -- priors -- are typically chosen to eliminate theoretically implausible solutions (an extreme example might be if all of the mass lies in one corner of the lens model space, or if the mass fluctuates wildly on the smallest scales probed). Such priors are typically far less restrictive than the implicit constraints inherent in parametric mass modelling.}

In this paper, we use a new non-parametric strong lens modelling framework -- 
\Glass\ -- to determine what combination of lensing, stellar mass, and
stellar kinematic constraints best constrain the projected mass profile and
shape of a gravitational lens. Some significant work has already proceeded in this direction in the literature.
\citet{2007ApJ...667..645R} were the first to test the recovery of strong
lensing surface density profiles using mock data generated from N-body models
{\bf JR. Is this true?}. They found that when including time delays, circularly
averaged surface density distributions can sufficiently well-recovered to make
interesting comparisons with theoretical models\footnote{Cosmological
parameters, however, are more sensitive. \citet{2007ApJ...667..645R} found that
over-restrictive model assumptions can lead to significant bias on the Hubble
parameter, $H_0$, for example, explaining earlier tensions reported in the
literature \citep[e.g.][]{2002ApJ...578...25K,2002astro.ph..4043K}.}. Since then, several groups
have used N-body mock data to explore the fidelity of strong lensing
reconstructions \citep{2007MNRAS.380.1729L, CITES}. We expand on these earlier
works by considering not only the recovery of the circularly averaged surface density profile
of a lens, but also its shape, higher order measures of the mass recovery (a
pixel-by-pixel comparison), and the utility of wrapping in
constraints from stellar mass estimates and/or stellar kinematics.

@@

The lens equation:
%
\begin{equation}
\vec\beta = \vec\theta - \frac{D_{LS}}{D_S}\vec\alpha(\vec\theta)
\label{eqn:lens_equation}
\end{equation}
%
maps an observed image position $\vec\theta$ to a source position $\vec\beta$
via the correction factor \citep[e.g.][]{1992grle.book.....S}:
%
\begin{equation}
\vec\alpha(\vec\theta) = \frac{4GD_L}{c^2} \int \Sigma(\vec\theta')\frac{(\vec\theta - \vec\theta')}{\ |\vec\theta - \vec\theta'|^2}d^2\vec\theta'
\end{equation}
%
which accounts for the gravitational lensing effect of an intervening mass
(where $G$ is Newton's gravitational constant, and $c$ is the speed of light).
For our purposes we make use of the thin mass sheet approximation and assume
that the lensing mass is infinitely thin compared with the distance between the
source and the lens $D_{LS}$ and the lens and the observer $D_{L}$. These are
angular diameter distances where $D_* = (c/H_0)d_*$, $H_0$ is the Hubble constant, and $d_*$ is a
dimensionless number that depends on cosmology.  The lens can then be thought
of as a projected surface density $\Sigma$ which diverts the path of a photon
instantaneously through the bending angle $\vec\alpha$.

@@

One way to understand the lens equation is via Fermat's principle. We can think of light as travelling only 
along extremum paths where lensed images occur \citep{1986ApJ...310..568B}. Such paths occur at the extrema of the photon {\it arrival time surface} $t(\vec\theta)$ that depends on the geometric path the photon takes and the general relativistic gravitational time dilation
due to a thin lens at redshift $z_L$. In its complete form, with all units
and cosmology included, we have \citep{1986ApJ...310..568B}:
%
\begin{eqnarray}
N^2ct(\vec\theta) & = & (1+z_L)\frac{D_{L}D_{S}}{D_{LS}}\frac12 |\vec\theta - \vec\beta|^2 \nonumber \\
& & - (1+z_L)\frac{4GD_{L}^2}{c^2}\int \Sigma(\vec\theta') \ln |\vec\theta-\vec\theta'| d^2\vec\theta'
\label{eqn:full_arrival_time}
\end{eqnarray}
%
where the factor of $D_L^2$ in the second term comes from the fact that $\Sigma$
has units of \Msun/lyr$^2$. We can clean this up by writing down a dimensionless time
delay:
%
\begin{equation}
\tau = \left[ (1+z_L) d_L\right]^{-1}\nu t
\label{tau}
\end{equation}
%
in terms of our previous definitions. If we
further define a dimensionless density:
%
\begin{equation}
\kappa_\infty = \frac{4\pi G}{c^2}\frac{c}{H_0}d_L\Sigma
              = \frac{d_L}{\nu}\Sigma
\end{equation}
%
and a lensing potential:
%
\begin{equation}
\psi(\vec\theta) = \frac1\pi \int \kappa_\infty(\vec\theta') \ln|\vec\theta - \vec\theta'| d^2\vec\theta'\
\label{lensing potential}
\end{equation}
%
we can express \eqnref{eqn:full_arrival_time} very compactly as:
%
\begin{equation}
\tau(\vec\theta) = \frac12 \xi |\vec\theta-\vec\beta|^2 - \psi(\vec\theta)
\label{arrival time}
\end{equation}
%
where $\xi \equiv D_{S}/D_{LS}$. We explicitly write $\kappa_\infty$ to remind ourselves
that there is no source distance factor involved. This will be useful later when we consider
multiple sources. Notice that the constraint $\nabla \tau = 0$ -- i.e. extrema in the arrival time surface -- recovers the lens equation (\eqnref{eqn:lens_equation}).

The only lensing observables from \eqnref{arrival time} are the image positions. However,  if the source object is
variable then the observed light curves of each image will be
identical but shifted in time due to the different photon path lengths.
The time difference between identical portions of the light curves is called
the time delay $\Delta t$ between images.  Using \eqnref{tau} the time delay
$\Delta t_{21}$ between two images $\vec\theta_1$ and $\vec\theta_2$, where $\vec\theta_2$
arrives after $\vec\theta_1$, is $\Delta t_{21} = \Delta \tau_{21}(1+z_L)d_L /
\nu$. If $\beta$ and $\kappa_\infty$ could be known exactly this would allow one
to precisely infer the angular diameter distance to the lens and thus -- via a cosmological model -- the Hubble constant. However, the source position is not
observable and the density distribution is highly degenerate.

@@

The trouble with solving the lens equation for the mass distribution is that the solutions are not unique. To see why this is, it is instructive to simplify \eqnref{eqn:lens_equation} for a circularly symmetric lens: 
%
\begin{equation}
\vec\beta = \vec\theta - \frac{\theta_E^2}{\theta^2}\vec\theta
\label{eqn:lens_equation_circ}
\end{equation}
%
where $\theta = |\vec\theta|$, $\theta_E^2 = \frac{D_{LS}}{D_S D_L} \frac{4 GM(<\theta)}{c^2}$ is the Einstein radius, and $M(<\theta)$ is the mass enclosed within the images.

For on-axis sources (\vec\beta\ = \vec0), the images split into a degenerate Einstein ring with $\theta = \theta_E$. Even in this situation of maximal information (since the source position $\vec\beta$ cannot typically be known), there is a trivial degeneracy between $M(<\theta_E)$ and the angular diameter distance. For fixed cosmology and in the most ideal situation, a single source splitting into images gives us only an enclosed mass. This `steepness' degeneracy (also known as the mass-sheet degeneracy) generalises to the non-circularly symmetric case \citep{1985ApJ...289L...1F,2000AJ....120.1654S}. Thus, to measure the mass profile of a lens, we require more information. This can come in the form of sources at different redshifts -- since each has its own Einstein radius, each constrains a different enclosed mass $M(<\theta_E')$. Or it can come in the form of additional constraints like time delay data between the images, stellar mass estimates from stellar populations synthesis modelling \citep{2008MNRAS.383..857F}, stellar kinematics \citep{2002MNRAS.337L...6T}, or similar. However, even with further information, higher order degeneracies remain. \citet{2008MNRAS.386..307L} showed that there is a monopole degeneracy that allows additional mass to be deposited in-between images without any optical effect, while \citep{2006ApJ...653..936S} find twisting/shape degeneracies that are sensitive to the time delays. Further degeneracies enter also if there is a strong {\it external} field acting on the lens -- for example from a larger group or cluster environment within which the lens sits \citep[e.g.][]{1996ApJ...468...17B}; this {\it shear term} can, in principle, however, be constrained by data \citep[e.g.][]{2002ApJ...578...25K}. In \secref{sec:results}, we will use \Glass\ to determine how well such degeneracies can be broken by data of ever-increasing quality to measure the mass profile and shape of a lens. We assume throughout that the shear is negligible.

\subsection{Stellar population synthesis modelling}

GOT TO HERE.

\subsection{Stellar kinematics}

@@

\Glass\ uses an adaptive grid of mass pixels
to model the lens, generating thousands of models to marginalise over
uncertainties. It shares some heritage with an earlier code, \PixeLens\
\citep{1997MNRAS.292..148S,2008ApJ...679...17C}, but differs in several
important respects:

This new functionality allows us to include non-lensing data constraints. Linear constraints -- like the stellar
mass -- are applied simultaneously with the strong lensing constraints;
non-linear constraints are applied in a post-processing step, where models are
rejected using a likelihood analysis. This latter was prohibitively expensive
with \PixeLens\ as only up to $\sim$1000 models could be generated in a
reasonable time. With \Glass, we can routinely generate hundreds of thousands
of models such that we can afford to discard some if they are inconsistent with
independent data.

@@

\begin{figure}
\plottwo{AAchi2_profile-full.pdf}{BBchi2_profile-full.pdf}

\plottwo{ACchi2_profile-full.pdf}{BCchi2_profile-full.pdf}
\caption{The main results showing the quality of model recovery. Each panel corresponds to 
the named mock galaxy, whose parameters are listed in \tabref{mock galaxy params}. Within
each panel are six groups of results for each of six lens morphologies. Each morphology
considered the presence of time delays and a central image. The black markers are for tests
that did not include the stellar mass as a lower bound constraint, while the red markers
indicate where the stellar mass has been given.}
\label{main results}
\end{figure}

@@

\plottwo{ACchi2_profile.pdf}{BCchi2_profile.pdf}
\caption{Profile $\chi$ with $1\sigma$ error bars.}
\label{main results}
\end{figure}

\begin{figure}
\plottwo{AAchi2-full.pdf}{BBchi2-full.pdf}

\plottwo{ACchi2-full.pdf}{BCchi2-full.pdf}
\caption{Pixel-wise $\chi$.}
\label{main results}
\end{figure}
